Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-21 2015-turklang-kazdep/paper.tex
verbal nouns ad advcl
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60956 72bbbca6-d526-0410-a7d9-f06f51895060

Verbal nouns allow a whole verb phrase to be used as a nominal, and the resulting verbal noun phrase may be used as a subject or object of a verb.  When used as the subject of a verb, verbal noun phrases receive the UD label \udtag{subj} and when the object of a verb \udtag{ccomp}.  An example of a verbal noun phrase used as a \udtag{ccomp} dependency of the main verb is given in table~\ref{fig:gerdat}.

@@

>>>>

Verbal nouns allow a whole verb phrase to be used as a nominal, and the resulting verbal noun phrase may be used as a subject or object of a verb.  When used as the subject of a verb, verbal noun phrases receive the UD label \udtag{subj}.  When used as the object of a verb, verbal noun phrases receive the UD label \udtag{ccomp}, unless the subject of the subordinate clause is obligatorily identical to the subject of the main clause, in which case it receives \udtag{xcomp}.  An example of a verbal noun phrase used as a \udtag{ccomp} dependency of the main verb is given in table~\ref{fig:gerdat}.

@@

As mentioned earlier, verbal nouns combined with certain case morphology and/or postpositions can function as an adverbial adjunct to a main clause, similar to verbal adverb clauses.  In such instances, they receive the UD label \udtag{advcl}, and example of which is given in figure~\label{fig:gerabl}.
